Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-10 podc16/paper2.tex
work on paper2.tex

A dependency-set computation algorithm exposes the input actions ${\operatorname{announce}\left( c \right)}^p$, where $c$ is a command, and the output actions ${suggest\left( c, deps \right)}^p$, where $c$ is a command and $deps$ is a set of commands.
Moreover, a dependency-set computation algorithm must ensure that:
\begin{itemize}[noitemsep,nolistsep]
    \item For any suggestion ${suggest\left( c, deps \right)}$, every command in $c\cup deps$ must have been announced before.
    \item for any two suggestions $suggest\left( c_1, deps_1 \right)$ and $suggest\left( c_2, deps_2 \right)$,  if $c_1$ and $c_2$ do not commute then either $c_1\in deps_2$ or $c_2 \in deps_1$.
\end{itemize}

>>>>

A dependency-set computation algorithm exposes the input actions ${\operatorname{announce}\left( c \right)}^p$, where $c$ is a command, and the output actions ${suggest\left( c, deps \right)}^p$, where $c$ is a command and $deps$ is a set of commands.
Moreover, a dependency-set computation algorithm must ensure that:
\begin{itemize}[noitemsep,nolistsep]
    \item For any suggestion ${suggest\left( c, deps \right)}$, every command in $c\cup deps$ must have been announced before.
    \item for any two suggestions $suggest\left( c_1, deps_1 \right)$ and $suggest\left( c_2, deps_2 \right)$,  if $c_1$ and $c_2$ do not commute ($\left( c_1,c_2 \right) \in R$) then either $c_1\in deps_2$ or $c_2 \in deps_1$.
\end{itemize}
